Locally-Oriented Programming:\\ A Simple Programming Model for Stencil-Based Computations on Multi-Level Distributed Memory Architectures

### 2015-01-31 papers/LOPe/local.tex
Changes as suggested by Daniel.
Fixed Dan's email address.
Slight modification to keyword list.

\usepackage{url}
\urldef{\mailsa}\path|rasmus@uoregon.edu, mjsottile@computer.org,|
\urldef{\mailsb}\path|dannagle@verizon.net, soren.rasmussen@aggiemail.usu.edu|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

\author{Craig Rasmussen
\and Matthew Sottile\and Dan Nagle\and Soren Rasmussen}

@@

\keywords{domain specific language, stencil compilers, distributed memory parallelism}
\end{abstract}

>>>>

\usepackage{url}
\urldef{\mailsa}\path|rasmus@uoregon.edu, mjsottile@computer.org,|
\urldef{\mailsb}\path|dangle@ucar.edu, soren.rasmussen@aggiemail.usu.edu|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

\author{Craig Rasmussen
\and Matthew Sottile\and Daniel Nagle\and Soren Rasmussen}

@@

\keywords{domain specific language, stencil compiler, distributed memory parallelism}
\end{abstract}
